Proof nets for first-order additive linear logic

### 2018-03-23 Archive/ALL1-backup-4.tex
some cleanup

\documentclass{article}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{proof}
\usepackage{stmaryrd}
\usepackage{xargs}

@@

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\theoremstyle{plain}
\newtheorem{lemma}[definition]{Lemma}

@@

\newcommand\subs[1]{\textsc{sub}(#1)}

@@

@@

@@

@@

@@

\begin{figure}
\hrule
\par\bigskip
\[
	\infer{\seq P{\dual P}}{}
\qquad
	\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}
\qquad
	\infer{\seq A{B\*C}}{\seq AB && \seq AC}
\]
\par
\[
	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
\qquad
	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
\]
\par
\[
	\infer{\seq A{\dual A}}{}
\qquad
	\infer{\seq AC}{\seq AB && \seq{\dual B}C}
\]
\par\bigskip\hrule
\caption{A sequent calculus for $\all1$}
\label{fig:sequent calculus}
\end{figure}

@@

First-order terms and the formulas of first-order $\all$ are generated by the following grammars.
%
\setMidspace{5pt}
\[
\begin{array}{l@{}l}
	t &\Coloneqq a \Mid x \Mid f(t_1,\dots,t_n)
\\[10pt]
	P &\Coloneqq p(t_1,\dots,t_n) \Mid \dual p(t_1,\dots,t_n)
\\[10pt]
	A &\Coloneqq P \Mid A\+A \Mid A\*A \Mid \exists x.A \Mid \forall a.A
\end{array}
\]
%
Negation $(\dual{\,\cdot\,})$ is applied to predicate symbols, $\dual p$, as a matter of convenience. The \defn{dual} $\dual A$ of an arbitrary formula $A$ is given by DeMorgan. We use the following notational conventions.
%
\\[2\itemsep]
%
\begin{tabular}{@{}lll@{}}
	$a,b,c$ & $\in \varA$ 		& universally quantified variables (and free variables)\\
	$x,y,z$ & $\in \varE$		& existentially quantified variables \\
	$f,g,h$ & $\in \Sigma_f$	& $n$-ary $(n\geq 0)$ function symbols from a fixed alphabet $\Sigma_f$\\
	$p,q,r$ & $\in \Sigma_p$	& $n$-ary $(n\geq 0)$ predicate symbols from a fixed alphabet $\Sigma_p$ \\
	$s,t,u$ & $\in \terms$ 		& first-order terms over $\varA$, $\varE$, $\Sigma_f$, and $\Sigma_p$ \\
	$P,Q,R$ & $\in \atom$		& atomic propositions \\
	$A,B,C$ & $\in \all1$		& formulas \\
\end{tabular}
%
\\[2\itemsep]
%
A \defn{sequent} $\seq AB$ is an ordered pair of formulas $A$ and $B$. A sequent calculus for \all1 is given in Figure~\ref{fig:sequent calculus}, where each rule has a symmetric counterpart that applies to the first formula in the sequent. We write $\prf\Pi AB$ for a proof $\Pi$ with conclusion sequent $\seq AB$. Anticipating the requirements of proof nets, we will assume the following convention for \all1 proofs.

@@

By a \defn{subformula} we will mean a subformula \defn{occurrence}. For instance, a formula $A\*A$ has two subformulas $A$, one on the left and one on the right. The \defn{subformulas} $\subs A$ of a formula are given by
\[
	\subs A = \{A\} \cup
	\left\{\begin{array}{ll}
		\subs B\uplus\subs C	& \text{if $A=B\+C$ or $A=B\*C$} \\[5pt]
		\subs B					& \text{if $A=\exists x.B$ or $A=\forall a.B$}
	\end{array}\right.
\]
We will write $B\sub A$ if $B$ is a subformula of $A$.

In the context of a sequent $\seq AB$, a \defn{link} $(A',B')$ is a pair of subformulas $A'\leq A$ and $B'\leq B$. A link is an \defn{axiom link} if both formulas are atomic propositions. A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on $\seq AB$. %It is an \defn{axiom linking} if all links are axiom links.

@@

A \defn{witness map} $\sigma$ is a substitution map
\[
	\sigma\colon \varE \to \terms
\]
which assigns terms to existential variables. We write $\varnothing$ for the empty map (the identity). The map $\sigma[x\mapsto t]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else, while $\sigma\minus x$ is the identity on $x$ and otherwise as $\sigma$. The application of a witness map $\sigma$ to a formula $A$ is written $A\sigma$.

A \defn{labelled link} $\clink AB$ is a link carrying a witness map $\sigma$. A \defn{labelled linking} respectively a \defn{labelled pre-net} is a linking or pre-net where every link is labelled. A labelled linking $\lambda$ reverts to an unlabelled one, written $\floor\lambda$, by dropping the label of each link.

\begin{definition}
The \defn{labelled de-sequentialization} of a sequent proof $\prf\Pi AB$ is the labelled pre-net $\net{\deseq[\varnothing]\Pi AB} AB$ where $\deseq-AB$ is defined as follows.
%
\[
\begin{array}{ccl}
	\Deseq{\infer{\seq P{\dual P}}{}}QR &=& \{\clink QR\}
\\ \\
	\Deseq{\infer {\seq A {B_0\+B_1}} {\deduce [\rule{0pt}{1pt}] {\seq A{B_i}} \Pi }}
	  {A'}{B_0'\+B'_1} 
	&=& \Deseq{\deduce[\rule{0pt}{1pt}]{\seq A{B_i}}\Pi}{A'}{B_i'}
\\ \\
	\Deseq{\infer{\seq A{B\*C}}{
	  \deduce[\rule{0pt}{1pt}]{\seq AB}\Pi 
	  && 
	  \deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}}{A'}{B'\*C'}
	&=& \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
	  \cup
	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}{A'}{C'}
\\ \\
	\Deseq{\infer{\seq A{\exists x.B}}{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}}
	  {A'}{\exists x.B'}
	&=&
	 \Deseq[{\sigma[x\mapsto t]}]{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}
	  {A'}{B'}
\\ \\
	\Deseq{\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]
	  {\seq A{\forall a.B}}{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}}{A'}{\forall a.B'}
	&=&
	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
\end{array}
\]
The \defn{(unlabelled) de-sequentialization} of $\Pi$ is $\net{\floor\Pi_{A,B}}AB$ where $\floor\Pi_{A,B}$ is $\floor{\deseq[\varnothing]\Pi AB}$.
\end{definition}

To generate witness maps for an unlabelled linking, we will be using unification. A \defn{unifying} witness map $\sigma$ for formulas $A$ and $B$ is one such that $A\sigma=B\sigma$. Note that these will substitute only the free existential variables, but not bound ones or universal variables. For instance, the only unifying witness map of $p(x,y)$ and $p(a,a)$ is $\{x\mapsto a,y\mapsto a\}$, while $\exists y.p(x,x)$ and $\exists y.p(a,y)$ have no unifier.

A witness map $\sigma$ is \defn{more general} than $\tau$, witten $\sigma\leq\tau$, if there is a $\rho$ such that $(A\sigma)\rho = A\tau$ for any $A$. The \defn{join} $\sigma\join\tau$ of two maps $\sigma$ and $\tau$ is the least map $\rho$ such that $\sigma\leq\rho$ and $\tau\leq\rho$, if it exists. If it does, we call $\sigma$ and $\tau$ \defn{compatible}, written $\sigma\comp\tau$.

The \defn{initial witness map} $\sigma(A,B)$ is the most general unifying witness map for the formulas $A$ and $B$, if it exists; if it does, $A$ and $B$ are \defn{compatible}. An unlabelled axiom link $(P,Q)$ is \defn{compatible} if $P$ and $\dual Q$ are compatible; a labelled one $\clink PQ$ is \defn{compatible} if $\sigma$ is a unifier for $P$ and $\dual Q$. A (labelled) linking or pre-net is \defn{compatible} if all links are compatible axiom links. The \defn{initial labelling} of a compatible linking $\lambda$ or pre-net $\net\lambda AB$ is the labelled linking $\lambda_\star$ or labelled pre-net $\net{\lambda_\star}AB$ given by
\[
	\lambda_\star = \{~\clink[\sigma(P,\dual Q)]PQ~\mid~(P,Q)\in\lambda~\}~.
\]
%Observe that $\floor{\lambda_\star}=\lambda$. We call $\floor\lambda_\star$ the \defn{initial re-labelling} of a labelled linking $\lambda$, and analogously for a pre-net $\net\lambda AB$.

@@

\begin{figure}
\hrule
\par\bigskip
\[
\begin{array}{rcl@{\hspace{40pt}}rcl} 
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{B\+C}
    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{1,1}
    \end{tikzpicture}}
&\rightsquigarrow& 
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{B\+C}
    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
    \end{tikzpicture}}
&    
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{\exists x.B}
    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
    \end{tikzpicture}}
&\rightsquigarrow&
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{\exists x.B}
    	\Vlink[red,label={~$\scriptstyle{\sigma\!\minus\!x}$}]{1,1}
    \end{tikzpicture}}
\\ \\    
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{B\*C}
    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{[-1]1,1}
    	\Vlink[red,label={~$\scriptstyle\tau$}]{[1]1,3}
    \end{tikzpicture}}
&\stackrel{\sigma\comp\tau}\rightsquigarrow&   
	\vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{B\*C}
    	\Vlink[red,label={~$\scriptstyle{\sigma\cup\tau}$}]{1,2}
    \end{tikzpicture}}
&  
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{\forall a.B}
    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
    \end{tikzpicture}}
&\stackrel{a\,\notin\,\fv(A\sigma)}\rightsquigarrow&
    \vc{\begin{tikzpicture}[net]
    	\formula[y=2]{A}
    	\formula[y=1]{\forall a.B}
    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,1}
    \end{tikzpicture}}
\end{array}
\]
\par\bigskip\hrule
\caption{Coalescence rules}
\label{fig:coalescence}
\end{figure}

>>>>

\documentclass[UKenglish]{lipics-v2016}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{latexsym}
\usepackage{microtype}
\usepackage{proof}
\usepackage{stmaryrd}
\usepackage{xargs}

@@

\bibliographystyle{plainurl}

% ============================== MACROS

\makeatletter

@@

\newcommand\subs[1]{\textsc{sub}(#1)}
\newcommand\dom[1]{\textsc{dom}(#1)}

@@

\newcommand\ult{\subseteq}
\newcommand\uco{\smallfrown}
\newcommand\ujn{\cup}

\newcommand\vlt{\le}
\newcommand\vco{\mathrel{\makebox[5pt][c]{\raisebox{-1ex}{$\widehat{}$}}}}
\newcommand\vjn{\vee}

@@

\newcommand\ucoal{\leadsto}
\newcommand\vcoal{\rightsquigarrow}

\newcommand\urr[1]{
  \ifx#1+\expandafter\@urr\else
  \ifx#1*(\*)\else
  \ifx#1!(\forall)\else
  \ifx#1?(\exists)\else
  (#1)
  \fi\fi\fi\fi
}
\newcommand\@urr[1]{(+_{#1})}
\newcommand\vrr[1]{
  \ifx#1+\expandafter\@vrr\else
  \ifx#1*\langle\*\rangle\else
  \ifx#1!\langle\forall\rangle\else
  \ifx#1?\langle\exists\rangle\else
  \langle#1\rangle
  \fi\fi\fi\fi
}
\newcommand\@vrr[1]{\langle+_{#1}\rangle}

@@

% ===== Derivations

\newcommand\udn{\mathrel{\rotatebox[origin=c]{-90}{$\ucoal$}\kern1pt}}
\newcommand\vdn{\mathrel{\rotatebox[origin=c]{-90}{$\vcoal$}}}

\newcommandx\ujg[4][2=\sigma]{#1\udn\clink[#2]{#3}{#4}}	%{#2\udn_{#1}{#3}\mathbin,{#4}}
\newcommandx\vjg[4][2=\sigma]{#1\vdn\clink[#2]{#3}{#4}}	%{#2\vdn_{#1}{#3}\mathbin,{#4}}

\makeatother

% ============================== TITLE & AUTHORS

\title{Proof nets for first-order additive linear logic}
%\titlerunning{Proof nets for ALL1}

\author[1]{Willem B.\ Heijltjes}
\author[2]{Dominic J.D.\ Hughes}
\author[3]{Lutz Stra\ss burger}
\affil[1]{University of Bath, United Kingdom\\
  \texttt{w.b.heijltjes@bath.ac.uk}}
\affil[2]{
  \texttt{}}
\affil[3]{INRIA \&\ \'Ecole Polytechnique, Palaiseau, France\\
  \texttt{lutz.strassburger@inria.fr}}
\authorrunning{W.B.\ Heijltjes, D.J.D.\ Hughes, and L.\ Stra\ss burger}

\Copyright{Willem B.\ Heijltjes, Dominic J.D.\ Hughes, and Lutz Stra\ss burger}

\subjclass{Dummy classification -- please refer to \url{http://www.acm.org/about/class/ccs98-html}}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
\keywords{Linear logic, Proof nets}

% ============================== CONTENT

@@

\subsection{Sequentialization}

\[
	\infer{\seq P{\dual P}}{}
\qquad
	\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}
\qquad
	\infer{\seq A{B\*C}}{\seq AB && \seq AC}
\qquad
	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
\qquad
	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
\]

\[
	\infer[\!\!\scriptstyle{Q\sigma=\dual R\sigma}]{\ujg{\clink QR}QR}{}
\]

\[
	\infer[\!\!\scriptstyle{\sigma\,=\,\sigma(Q,R)}]{\vjg{\clink[]QR}QR}{}
\]

\[
	\infer{\ujg\lambda A{B_0\+B_1}}{\ujg\lambda A{B_i}}
\]

\[
	\infer{\vjg\lambda A{B_0\+B_1}}{\vjg\lambda A{B_i}}
\]

\[
	\infer[\!\!\scriptstyle{\sigma\,\uco\,\tau}\vphantom)]{\ujg{\lambda\cup\kappa}[\sigma\ujn\tau]A{B\*C}}{\ujg\lambda[\sigma]AB && \ujg\kappa[\tau]AC}
\]

\[
	\infer[\!\!\scriptstyle{\sigma\,\vco\,\tau}\vphantom)]{\vjg{\lambda\cup\kappa}[\sigma\vjn\tau]A{B\*C}}{\vjg\lambda[\sigma]AB && \vjg\kappa[\tau]AC}
\]

\[
	\infer{\ujg\lambda[\sigma\!\minus\!x]A{\exists x.B}}{\ujg\lambda AB}
\]

\[
	\infer{\vjg\lambda[\sigma\!\minus\!x]A{\exists x.B}}{\vjg\lambda AB}
\]

\maketitle

\begin{abstract}

\end{abstract}

\subsection{Proof identity}

\[
	\infer={\exists x.p(x),\exists y.\dual p(y)}{\infer{p(t),\dual p(t)}{}}
	\quad
	\stackrel?\equiv
	\quad
	\infer={\exists x.P(x),\exists y.\dual p(y)}{\infer{p(s),\dual p(s)}{}}
\]

\[
	\infer{\exists x.p,\dual p}{\infer{p[t/x],\dual p}{}}
	\quad
	\stackrel?\equiv
	\quad	
	\infer{\exists x.p,\dual p}{\infer{p[s/x],\dual p}{}}
\]

\[
	\infer{\exists x.p\+q(x),\dual p}{\infer{p\+q(t)}{\infer{p,\dual p}{}}}
	\quad
	\stackrel?\equiv
	\quad	
	\infer{\exists x.p\+q(x),\dual p}{\infer{p\+q(s)}{\infer{p,\dual p}{}}}
\]

@@

\begin{figure}
\[
	\infer{\seq P{\dual P}}{}
\qquad
	\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}
\qquad
	\infer{\seq A{B\*C}}{\seq AB && \seq AC}
\qquad
	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
\qquad
	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
\]
\caption{A sequent calculus for $\all1$}
\label{fig:sequent calculus}
\end{figure}

@@

First-order terms and the formulas of first-order $\all$ are generated by the following grammars.
%
\setMidspace{5pt}
\[
\begin{array}{@{}l@{}l}
	t &\Coloneqq a \Mid x \Mid f(t_1,\dots,t_n)
\\[10pt]
	P &\Coloneqq p(t_1,\dots,t_n) \Mid \dual p(t_1,\dots,t_n)
\\[10pt]
	A &\Coloneqq P \Mid A\+A \Mid A\*A \Mid \exists x.A \Mid \forall a.A
\end{array}
\]
%
Negation $(\dual{\,\cdot\,})$ is applied to predicate symbols, $\dual p$, as a matter of convenience. The \defn{dual} $\dual A$ of an arbitrary formula $A$ is given by DeMorgan. We use the following notational conventions.
%
\[
\begin{tabular}{@{}lll@{}}
	$a,b,c$ & $\in \varA$ 		& universally quantified variables (and free variables)\\
	$x,y,z$ & $\in \varE$		& existentially quantified variables \\
	$f,g,h$ & $\in \Sigma_f$	& $n$-ary $(n\geq 0)$ function symbols from a fixed alphabet $\Sigma_f$\\
	$p,q,r$ & $\in \Sigma_p$	& $n$-ary $(n\geq 0)$ predicate symbols from a fixed alphabet $\Sigma_p$ \\
	$s,t,u$ & $\in \terms$ 		& first-order terms over $\varA$, $\varE$, $\Sigma_f$, and $\Sigma_p$ \\
	$P,Q,R$ & $\in \atom$		& atomic propositions \\
	$A,B,C$ & $\in \all1$		& formulas \\
\end{tabular}
\]
%
A \defn{sequent} $\seq AB$ is a pair of formulas $A$ and $B$. A sequent calculus for \all1 is given in Figure~\ref{fig:sequent calculus}, where each rule has a symmetric counterpart that applies to the first formula in the sequent. We write $\prf\Pi AB$ for a proof $\Pi$ with conclusion sequent $\seq AB$. Anticipating the requirements of proof nets, we will assume the following convention for \all1 proofs.

@@

By a \defn{subformula} we will mean a subformula \defn{occurrence}. For instance, a formula $A\*A$ has two subformulas $A$, one on the left and one on the right. The \defn{subformulas} $\subs A$ of a formula are defined as follows; we write $B\sub A$ if $B$ is a subformula of $A$, i.e.\ if $B\in\subs A$.
\[
	\subs A = \{A\} \cup
	\left\{\begin{array}{ll}
		\subs B\uplus\subs C	& \text{if $A=B\+C$ or $A=B\*C$} \\[5pt]
		\subs B					& \text{if $A=\exists x.B$ or $A=\forall a.B$}
	\end{array}\right.
\]

A \defn{witness map} $\sigma\colon \varE \rightharpoonup \terms$ is a substitution map which assigns terms to existential variables, given as a partial function. The \defn{empty} witness map $\varnothing$ is the everywhere undefined partial function. The map $\sigma[x\mapsto t]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else.

A \defn{link} $\clink CD$ on a sequent $\seq AB$ is a pair of subformulas $C\leq A$ and $D\leq B$ along with a witness map $\sigma$. We assume the existential variables occurring in the range of $\sigma$ to be fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$. A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on it.% $\seq AB$.

@@

An \defn{axiom} link is a link $\clink PQ$, and a linking consisting of only axiom links an \defn{axiom linking}.
%
A link is \defn{clean} if its witness map is empty, $\clink[\varnothing]CD$; it may then be rendered simply $(C,D)$. A linking or pre-net is \defn{clean} if all its links are. We write $\floor\lambda$ respectively $\floor{\net\lambda AB}$ for the clean version of a linking or pre-net, which forgets the witness map for each link.
%
A link is \defn{strict} if its domain consists of exactly the existentially quantified variables that its formulas are in scope of. That is, a link $\clink CD$ in a pre-net $\net\lambda AB$ is strict if
\[
	\dom\sigma = \{\,x \mid C < \exists x.X \leq A\,\}
			\cup \{\,y \mid D < \exists y.Y \leq B\,\}~.
\]
A linking or pre-net is \defn{strict} if all its links are.

\begin{definition}
The \defn{de-sequentialization} $[\Pi]$ of a sequent proof $\prf\Pi AB$ is the pre-net $\net{\deseq[\varnothing]\Pi AB} AB$ where $\deseq-AB$ is defined as follows.
%
\[
\begin{array}{ccl}
	\Deseq{\infer{\seq P{\dual P}}{}}QR &=& \{\clink QR\}
\\ \\
	\Deseq{\infer {\seq A {B_0\+B_1}} {\deduce [\rule{0pt}{1pt}] {\seq A{B_i}} \Pi }}
	  {A'}{B_0'\+B'_1} 
	&=& \Deseq{\deduce[\rule{0pt}{1pt}]{\seq A{B_i}}\Pi}{A'}{B_i'}
\\ \\
	\Deseq{\infer{\seq A{B\*C}}{
	  \deduce[\rule{0pt}{1pt}]{\seq AB}\Pi 
	  && 
	  \deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}}{A'}{B'\*C'}
	&=& \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
	  \cup
	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}{A'}{C'}
\\ \\
	\Deseq{\infer{\seq A{\exists x.B}}{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}}
	  {A'}{\exists x.B'}
	&=&
	 \Deseq[{\sigma[x\mapsto t]}]{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}
	  {A'}{B'}
\\ \\
	\Deseq{\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]
	  {\seq A{\forall a.B}}{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}}{A'}{\forall a.B'}
	&=&
	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
\end{array}
\]
The \defn{clean} de-sequentialization $\floor\Pi$ of $\prf\Pi AB$ is $\floor{[\Pi]}$.
\end{definition}

Observe that the pre-net $[\Pi]$ has a strict axiom linking and $\floor\Pi$ a clean axiom linking.

\subsection{Witness maps}

We will write $A\sigma$ for the application of the witness map $\sigma\colon\varE\rightharpoonup\terms$ to the formula $A$ as a substitution map. The \defn{composition} of two maps is written $\sigma\tau$, where $A(\sigma\tau)=(A\sigma)\tau$. The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$, and $\sigma|X$ is as $\sigma$ on the set of variables $X$ and undefined otherwise. We define the following further operations on witness maps.

\[
\begin{tabular}{@{}lp{.75\textwidth}@{}}
	$\sigma\ult\tau$
&
	A witness map is \defn{included} in another, $\sigma\ult\tau$,
	if for every $x\in\varE$, $\sigma(x)=t$ implies $\tau(x)=t$.
\\[5pt]	
	$\sigma\uco\tau$
&
	Two witness maps are \defn{coherent}, $\sigma\uco\tau$,
	if for every $x\in\varE$, if $\sigma(x)$ and $\tau(x)$
	are both defined then $\sigma(x)=\tau(x)$.
\\[5pt]
	$\sigma\ujn\tau$
&
	The \defn{union} of two witness maps $\sigma\ujn\tau$
	is defined if they are coherent, and is the map taking
	$x$ to $\sigma(x)$ or $\tau(x)$ if either is defined.
\\[5pt]
	$\sigma\vlt\tau$
&
	A witness map is \defn{more general} than another, 
	$\sigma\vlt\tau$, if there is a map $\rho$ such that 
	$\sigma\rho=\tau$.
\\[5pt]	
	$\sigma\vco\tau$
&
	Two witness maps are \defn{compatible}, $\sigma\vco\tau$,
	if there is a map $\rho$ such that $\sigma\rho=\tau\rho$.
\\[5pt]
	$\sigma\vjn\tau$
&
	The \defn{join} of two witness maps $\sigma\vjn\tau$ is defined
	if they are compatible, and is the least map $\rho$ such that
	$\sigma\vlt\rho$ and $\tau\vlt\rho$.
\end{tabular}%
\]

@@

We will define two \defn{coalescence} relations, one \defn{compounding} $(\ucoal)$ and one \defn{unifying} $(\vcoal)$.

\begin{definition}
\defn{Compounding coalescence} ($\ucoal$) is the rewrite relation on pre-nets generated by the following rules, which apply symmetrically to the first formula in the sequent.
%
\renewcommand{\+}{{+}}
\renewcommand{\*}{{\times}}
\begin{align}
  	\net{\{\clink AB\}}A{B\+C} 
& ~\ucoal~
	\net{\{\clink A{B\+C}\}}A{B\+C}
\tag{$\+_1$}
\\[5pt]
        \net{\{\clink AC\}}A{B\+C}
& ~\ucoal~  
	\net{\{\clink A{B\+C}\}}A{B\+C}
\tag{$\+_2$}
\\[5pt]
	\net{\{\clink AB,\clink[\tau]AC\}}A{B\*C}
& ~\ucoal~ 
	\net{\{\clink[\sigma\ujn\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\uco\tau
\tag{$\*$}
\\[5pt]	
	\net{\{\clink AB\}}A{\exists x.B}
& ~\ucoal~ 
	\net{\{\clink[\sigma\!\minus\!x]A{\exists x.B}\}}A{\exists x.B}
\tag{$\exists$}
\\[5pt]
	\net{\{\clink AB\}}A{\forall a.B}
& ~\ucoal~ 
	\net{\clink A{\forall a.B}}A{\forall a.B} \quad \text{if }a\,\notin\,\fv(A\sigma)
\tag{$\forall$}
\end{align}
%
\defn{Unifying coalescence} ($\vcoal$) is the rewrite relation generated by the following rules:
\[
	\vrr+1~,~\vrr+2~,~\vrr?~,~\vrr!
	\quad
	\text{are respectively as}
	\quad
	\urr+1~,~\urr+2~,~\urr?~,~\urr!
\]
plus the rule
\renewcommand{\+}{{+}}
\renewcommand{\*}{{\times}}
\begin{align}
	\net{\{\clink AB,\clink[\tau]AC\}}A{B\*C}
& ~\vcoal~ 
	\net{\{\clink[\sigma\vjn\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\vco\tau~.
\tag*{$\vrr*$}
\end{align}
%
A pre-net $\net\lambda AB$ \defn{coalesces}, in either relation $(\ucoal)$ or $(\vcoal)$, if it coalesces to a single clean link $\net{(A,B)}AB$. It \defn{strongly coalesces} if every coalescence sequence terminates at $\net{(A,B)}AB$.
\end{definition}

To be explicit, to generate coalescence as a rewrite relation means the following: a pre-net coalesces to another, $\net\lambda AB\ucoal \net{\lambda'}AB$ if and only if there is a rewrite rule $\net\kappa CD\ucoal\net{\kappa'} CD$ such that $C\leq A$, $D\leq B$, $\kappa\subseteq\lambda$, $\kappa'\subseteq\lambda'$, and $\lambda-\kappa=\lambda'-\kappa'$; and likewise for $(\vcoal)$.

\begin{definition}
An \all1 \defn{witnessing proof net} or \defn{witness net} is a pre-net $\net\lambda AB$ with a strict axiom linking $\lambda$, that compounding-coalesces.
\end{definition}

Coalescence on a clean axiom linking is initiated by assigning each link $(P,Q)$ an \defn{initial witness map} $\sigma(P,Q)$ which, if it exists, is the most general witness map $\sigma$ such that $P\sigma=\dual Q\sigma$. In other words, $\sigma(P,Q)$ is the most general unifier ($\textsc{mgu}$) of $P$ and $\dual Q$. If it exists, we call the link $(P,Q)$ \defn{compatible}, and a linking is \defn{compatible} if all its links are. For a compatible axiom linking $\lambda$ we define the \defn{initial witness assignment} $\lambda_\star$ to be:
\[
	\lambda_\star = \{~\clink PQ~\mid~(P,Q)\in\lambda~,~\sigma=\sigma(P,Q)~\}~.
\]

\begin{definition}
An \all1 \defn{unification proof net} or \defn{unification net} is a pre-net $\net\lambda AB$ with a clean, compatible axiom linking $\lambda$, such that $\net{\lambda_\star}AB$ unifying-coalesces.
\end{definition}

\subsection{Sequentialization}
